---
title: "Introduction to mrgsolve"
author: "Simulation Concepts Workshop<br>Metrum Research Group"
date: "ACoP10 2019"
---


<hr>

```{r setup, include=FALSE}
source("../common/global.R")
library(tidyverse)
theme_set(theme_bw())
library(mrgsolve)
```

# Read in a model 

- Meropenem population PK
  - IV administration, short or long infusion
  - 2-compartment PK

First, load `meropen_basic`, which is a PK model for meropenem, written 
in terms of basic PK parameters (e.g. `CL`, `V`, etc)

```{r}

```

Check the model parameters
```{r}

```

Check the model compartments

```{r}

```

View the model code

```{r}

```


# Explore dosing regimens with event object

We can use a simple event object to implement a single dose pf 
500 mg infused over 30 minutes


```{r}

```

The event object has data items like
1. `amt` : dose amount
1. `rate` : infusion rate
1. `cmt` : compartment number
1. `evid` : event id

There are other items as well. 


We can simulate from this event object with the `meropen_basic` model, 
running the simulation out to 8 hours
```{r}

```

Plot the result
```{r}

```


## Multiple dosing

Now, create an event object for 500 mg every 8 hours x 3 and simulate
a day of doses

```{r}

```


## Implement a batch of simulations

In addition to event objects, we can simulate a batch or population of 
individuals with a data set.  For example, to simulate the 500 mg 
at durations of 30 min, 1 hour and 3 hours, create a data set


```{r}

```

In this example, we have 3 IDs, each receiving 500 mg x1 and infusion durations
ranging from 0.5 to 3 hours.


Now to simulate the `meropen_basic` model with the data set

```{r}

```

A lot of the complexity and efficiency in your simulation comes from the 
data set.


# Population model

We can read in `meropen_pop`, which is a population version of the same
model

```{r}

```

Now, we have some population elements going

```{r}

```

check the random effects structure

```{r}

```

Now, when we make a population template, consisting of 50 subjects dosed at 
500 mg x1 over 2 hours

```{r}

```

we'll get population output

```{r}

```

# Three simulation workflows


## model + event

- Model: `meropen_basic.cpp`
- Event: 250 mg q8h x 5 d

```{r}

```

## model + data set

- Model: `meropen_pop.cpp`
- Covariates: CLCR 40, 100
- Data set: 
  - 500 mg q8h over 1 hr x 3 for 24 h if CLCR 100
  - 250 mg q8h over 1 hr x 3 for 24 h if CLCR 40


```{r}

```

### Some helper functions to create data sets


## model + event + idata_set

- Model: `meropen_pop.cpp`
- Covariates: WT
- Data set: 500 mg over 3 hours x1

```{r}

```


# Posterior simulation

Read in `post.csv`

```{r}

```

We can inventory the model

```{r, message=TRUE}
inventory(mod,post)
```


Form lists of OMEGA matrices
```{r}

```


Form lists of SIGMA matrices

```{r}

```

## Create a function to simulate one replicate

```{r}

```


## Create a loop to simulate 50 replicates

```{r}

```


# Parallelizing your code

Use the future.apply package

- Enable fork
- plan: multiprocess, workers 4

```{r}

```


